Covariant Phase Space\\[-.2ex]\large\it A Pedagogical Introduction

### 2021-06-24 alpha/CovariantPhaseSpace/charge.tex
Update Noether notes on background fields & more

% !TeX document-id = {b5392a94-51a3-49d1-9ba5-698bc09f9d35}
% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %

@@

\input{../preamble.tex}
\input{../.modules/basics/biblatex.tex}

@@

\addtocounter{section}{-1}
\section{Introduction \& Conventions}
	The phase space is understood as the space of \textit{all solutions} of the equations of motion (EoMs), satisfying the boundary conditions; alternatively, we can think of it as a collection of all possible \textit{initial configurations} of the system, and the additional \textit{symplectic structure} specifies their evolutions. This idea is best explained by \textcite{Crnkovic:1986ex}.

@@

	\begin{itemize}
	\item $\mcal{F}$ denotes the field space including \textbf{off-shell} configurations; the variation $\delta$ is assumed to be off-shell unless otherwise specified.

	\item $\tilde{\mcal{P}}$ denotes the field space including \textbf{on-shell} configurations only; one can then define a symplectic form $\omega$ on $\tilde{\mcal{P}}$, but it might be degenerate due to gauge redundancies;

	\item $\mcal{P}$ denotes the \textbf{physical phase space}, with a nice, non-degenerate sympletic structure.

@@

	\end{itemize}
%\smallskip
\textit{Diffeomorphism and stress tensor:}

	\begin{itemize}
	\item A infinitesimal diffeomorphism (diffeo) generated by vector field $\xi$ is given by:
	\begin{equation}
		x\mapsto x - \xi = x + \var_\xi {x},
	\quad
		\var_\xi {x}
		= -\xi,
	\quad
		\var_\xi \phi
		= X_\xi \cdot \var{\phi}
		= +\ldv{\xi} \phi,
	\end{equation}
	Here the sign convention is chose such that $\var_\xi \phi$ corresponds to a positive Lie derivative along $\xi$. Note that \cite{Banados:2016zim} chose a unconventional Lie derivative which contains a minus sign in its definition; we are \textit{not} going to follow that. In this convention the usual current for spacetime translation is given by:
	\begin{equation}
		\xi = -\pdd{\sigma},
	\quad
		j^\mu_\xi = j^\mu_{-\pdd{\sigma}}
		= T^{\mu\nu} \eta_{\nu\sigma}
		= T^{\mu\nu} (\pdd{\sigma})_\nu
	\label{eq:Noether_stress_convention}
	\end{equation}
	Where $T^{\mu\nu}$ is the Noether stress tensor.

	\item Wick rotation between Lorentzian and Euclidean signatures is defined such that:
	\begin{equation}
		\tau = it,
	\quad
		V^0_E = iV^0_L,
	\quad
		(\dd[D]{x})_E
		= i\,(\dd[D]{x})_L,
	\quad
		e^{iS_L} = e^{-S_E},
	\quad
		\mcal{L}_E
		= -\mcal{L}_L
	\label{eq:Wick_rotation}
	\end{equation}
	Where $
		S = \int \dd[D]{x} \sqrt{\abs{g}}\,\mcal{L}
	$ in both cases, and $V^0$ is the 0-th component of some $V^\mu$. Other scalar quantities, such as $
		g_{\mu\nu} V^\mu W^\nu
	$, are left invariant. This is the convention introduced in \textcite{Polchinski:1998rq}, Appendix A.

	For example, the Einstein-Hilbert action is given by:
	\begin{equation}
		S_L = \frac{1}{16\pi G_N}
			\int \sqrt{-g} \dd[D]{x} R,
	\quad
		S_E = -\frac{1}{16\pi G_N}
			\int \sqrt{g} \dd[D]{x} R
	\end{equation}
	For a closed Riemann surface in 2D, by Gauss--Bonnet theorem, we see that the Euclidean action is proportional to genus of the surface:
	\begin{equation}
		S_E = -\frac{1}{16\pi G_N}\,
			4\pi \chi(M)
		= -\frac{1}{4G_N}\,\chi(M),
	\quad
		\chi(M) = 2 - 2g,
	\quad
		e^{-S_E}
		\propto e^{-\frac{1}{2G_N} g}
	\end{equation}
	Note that in \textcite{Polchinski:1998rq}, the dilaton term in the Euclidean worldsheet action  goes like $+R\,\Phi(X)$, namely it's missing the minus sign; this is due to the convention for the dilaton $\Phi$: in the perturbative regime we have $\ave{\Phi} = \lambda < 0$, and thus $
		e^{-S_E} \sim e^{-\lambda \chi}
		\sim (g_c^2)^g
	$, where $
		g_c \sim e^\lambda < 1
	$ is the closed string coupling.

@@

	\item The Hilbert stress tensor is defined with the Lorentzian action:
	\begin{equation}
		T_{\mu\nu}(x)
		= - \frac{2}{\sqrt{-g}}
			\fdv{S_L}{g^{\mu\nu}(x)},
	\quad
		T^{\mu\nu}(x)
		= + \frac{2}{\sqrt{-g}}
			\fdv{S_L}{g_{\mu\nu}(x)}
	\end{equation}\\[-1.25\baselineskip]
	\begin{equation}
		\var{S_L}
		= \int \sqrt{-g} \dd[D]{x} 
			\pqty{
				-\frac{1}{2}\, T_{\mu\nu}
				\var{g^{\mu\nu}}
				+ \cdots
			}
		= \int \sqrt{-g} \dd[D]{x} 
			\pqty{
				+\frac{1}{2}\, T^{\mu\nu}
				\var{g_{\mu\nu}}
				+ \cdots
			}
	\end{equation}
	To understand the variational derivative here, we note that in the space of fields it's convenient to think of $x$ as an index to be contracted; the contraction is implemented by $
		\int \dd[D]{x}
	$, without the $\sqrt{\abs{g}}$ factor.

	An action can thus be thought of as the contraction between some fields and some operators with multiple $x$ ``indices'': $\Box_{x,x',\cdots}$. For example, we might have some bi-local operator $\Box_{x,x'}$ connecting $\phi(x)$ and $\phi(x')$. 
	In a \textit{local} action all these operators should be \textit{diagonal} in $x$, i.e.~$
		\Box_{x,x'} = \delta^D(x - x')\,\Box_x
	$.

@@

\pagebreak[4]
\section{Covariant formalism and Noether's theorem}
	The phase space is understood as the space of \textit{all solutions} of the equations of motion (EoMs), satisfying the boundary conditions; alternatively, we can think of it as a collection of all possible \textit{initial configurations} of the system, and the additional \textit{symplectic structure} specifies their evolutions. This idea is best explained by \textcite{Crnkovic:1986ex}.

	The inspiration comes from the Lagrangian treatment of field theory, where we work with:
	\begin{equation}
		\pi^\mu = \pdv{\mcal{L}}{(\pd_\mu\phi)}
	\end{equation}
	Which preserves general covariance. But $(\pi_\mu,\phi)$ is not a set of independent coordinates; they are constrained by the equations of motion (EoMs). The rough idea is that we start with $(\pi_\mu,\phi)$, and then reduce it to the independent variables $(\pi,\phi)$ by imposing the EoMs, and possibly, additional constraints due to gauge redundancy. 
\subsection{Off-shell variation on the field space}
	\noindent
	Let's start by considering a general action with boundary terms \cite{Harlow:2019yfa}:
	\begin{equation}
		S = \int_M L + \int_{\pd M} l,
	\quad
		L = \dd[D]{x} \sqrt{\abs{g}}\,\mcal{L}
	\end{equation}

	Variation $\var$ is now treated as an \textit{exterior derivative} on the space of fields. We can think of it as an \textit{enlarged} space with \textit{redundant variables} $(\pi_\mu,\phi)_I$, where $I$ labels all fields in the system. We have:
	\begin{equation}
		\var{S}
		= \int_M \var{L}
			+ \int_{\pd M} \var{l}
		= \int_M E_I \var{\phi^I}
			+ \int_{\pd M} \pqty{\Theta + \var{l}},
	\end{equation}
%	We've promoted $\phi^\mu$ to $\phi^I$ to include all fields, e.g.~the metric $g_{\mu\nu}$. 
	We've defined $\Theta$ which comes from the total derivative terms of the bulk $M$ variation, and we've performed an integration by parts and reduced $\int_M \dd{\Theta} = \int_{\pd M} \Theta$. Basically,
	\begin{empheq}{equation}
		\var{L}
		= E_I \var{\phi^I} + \dd{\Theta}
	\end{empheq}
	\vspace{-.3\baselineskip}
	\begin{equation}
		({\cdots})_I \var{(\dd{\phi^I})}
		= ({\cdots})_I \dd{(\var{\phi^I})}
		\sim \dd{(\cdots \var{\phi})}
		= \dd{\Theta},
	\quad
		\Theta \sim ({\cdots})_I \var{\phi^I}
	\end{equation}

@@

	Note that $\mcal{F}$ \textbf{includes possible ``background'' fields $\phi^B$} such as the fixed metric $g^{\mu\nu}$ for a field theory defined on a curved spacetime. These fields are fixed on-shell and therefore are absent in $\tilde{\mcal{P}}$.

@@

	What we've done here is simply a rewrite of the usual variation procedure; we just re-think it as a differential in the field space. To get to the physical phase space, we \textbf{suppress the variation of ``background'' fields $\phi^B$}, and then require the action to be \textbf{stationary, up to terms in the future / past boundary $\Sigma^\pm$:}
	\begin{empheq}{equation}
		\var{\phi^B}|_{\tilde{\mcal{P}}}
		= 0,
	\quad
		\var{S}|_{\tilde{\mcal{P}}}
		= \int_{\Sigma^+} ({\cdots})
			- \int_{\Sigma^-} ({\cdots})
		= \int_{\Sigma^\pm} ({\cdots})
	\end{empheq}
%\pagebreak[4]

	This differs slightly from what we are used to in most physics literature, where we simply set $\var{S} = 0$ to find the EoMs. The reason is that in physics, we usually impose the initial \& final conditions, or in other words, in \& out states, and the variation at $\Sigma^\pm$ is \textit{required} to vanish: $\var{\phi}|_{\Sigma^\pm} = 0$. Consider the simplest example: the (0+1)\,D worldline action of a point particle; we have:
	\begin{equation}
		S = \int L = \int \dd{t} \mcal{L},
	\quad
		\var{S}
		= \int E_I(t) \var{q^I(t)}
			+ \Theta\Big|^{\Sigma^+}_{\Sigma^-}
	\end{equation}
	\vspace{-.5\baselineskip}
	\begin{equation}
		E_I = \pqty{
			\pdv{\mcal{L}}{q^I}
			- \dv{t} \pdv{\mcal{L}}{\dot{q}^I}
		} \dd{t},
	\quad
		\Theta
		= \pdv{\mcal{L}}{\dot{q}^I} \var{q^I}
		= p_I \var{q^I},
	\quad
		p_I = \pdv{\mcal{L}}{\dot{q}^I}
	\end{equation}
	Traditionally, we impose $\var{q^I}|_{\Sigma^\pm} = 0$ as we fix the in \& out states, and then we find the EoMs $E_I = 0$. 
	However, this is slightly clumsy to implement in our new language, since $\var{\phi}$ is now a differential form in the phase space. We thus simply require that $\var{S}|_{\tilde{\mcal{P}}}$ vanish up to boundary terms at $\Sigma^\pm$, which achieve the same result.

	Generally, we have:
	\begin{equation}
		\var{\phi^B}|_{\tilde{\mcal{P}}}
		= 0,
	\quad
		\var{S}|_{\tilde{\mcal{P}}}
		= \int_{\Sigma^\pm} ({\cdots})
	\quad\Longrightarrow\quad
		E_{I\ne B}|_{\tilde{\mcal{P}}} = 0,
	\quad
		\int_N \pqty{\Theta + \var{l}}_{\tilde{\mcal{P}}}
		= \int_{\Sigma^\pm} ({\cdots}),
	\end{equation}
	\vspace{-.8\baselineskip}
	\begin{equation}
		\pd M = N \cup \Sigma^+ \cup (-\Sigma^-),
	\end{equation}
	Here $N$ is the spatial boundary. 
	In this way we've obtained the subspace (submanifold) $\tilde{\mcal{P}}$ of solutions constrained by the EoMs. We are one step closer to the physical phase space; in fact this \textit{is} the physical phase space if there are no gauge redundancies in the fields.

	Besides the EoMs, the boundary integral at $N$ should also vanish; this means that \textbf{not all boundary conditions are consistent with the theory}. 
	In fact, $N$ is where the dual theory lives for many holographic systems, so one would imagine that it's highly non-trivial. Generally \cite{Harlow:2019yfa},
	\begin{equation}
		(\Theta + \var{l})_{\tilde{\mcal{P}},N}
		= \dd{C},
	\quad
		\dd{C}\colon\ %
		\text{some 1-form on $N \subset \pd M$},
	\label{eq:boundary_cond}
	\end{equation}
	\vspace{-.8\baselineskip}
	\begin{equation}
%	\Longrightarrow\ %
		\int_{N} (\Theta + \var{l})_{\tilde{\mcal{P}}}
		= \int_{\pd M} \dd{C}
			+ ({\cdots})
		= \int_{\pd \pd M = \varnothing} C
			+ ({\cdots})
		= 0
			+ \int_{\Sigma^\pm} ({\cdots})
	\end{equation}

@@

	We shall see that this formalism will help us avoid confusions with boundary terms, which is best explained by \textcite{Banados:2016zim}. Also, off-shell variation will be quite useful if we want to quantize our theory, where we have to integrate over off-shell configurations as well.

%\pagebreak
\subsection{Symmetry variation and the Noether current}
	To get back to the familiar Noether's procedure, we need only plug in (contract with) a vector field $X_\xi$ in the field space $\mcal{F}$, labeled by the symmetry $\xi$:
	\begin{equation}
		\var_\xi
		= X_\xi \cdot \var
		= \iota_{X_\xi} \var
	\colon\ \Omega^0_\delta(\mcal{F})
		\to \Omega^0_\delta(\mcal{F})
	\end{equation}
	$\xi\mapsto X_\xi$ is the representation of $\xi$ in the field space, and $\Omega^0_\delta(\mcal{F})$ denotes 0-forms, i.e.~functions on $\mcal{F}$. 
	As an example, for diffeomorphism (diffeo), the induced variation is given by:
	\begin{equation}
		x\mapsto x - \xi,
	\quad
		\var_\xi \phi
		= X_\xi \cdot \var{\phi}
		= \ldv{\xi} \phi,
	\quad
		X_\xi
		= \int_M \dd[D]{x}
			\pqty\big{\ldv{\xi} \phi^I(x)}
			\fdv{\phi^I(x)}
	\label{eq:symmetry_var_field}
	\end{equation}

@@

	By now we've written down the above expressions \eqref{eq:symmetry_var_field} covariantly on the off-shell field space $\mcal{F}$, in terms of the redundant coordinates $\phi^I$. However, we can still interpret it as a variation on $\tilde{\mcal{P}}$, by simple restriction. 
\pagebreak

	In fact, by the definition of a \textit{symmetry} $\xi$, we have the \textbf{off-shell symmetry variation}:
	\begin{empheq}{equation}
		\var_\xi {\phi^B}
		= 0,
	\quad
		\var_\xi S = X_\xi \cdot \var{S}
		= \int_{\Sigma^\pm} ({\cdots})
	\end{empheq}
	In other words, symmetries should act trivially on the background fields $\phi^B$, and its action in the field space is characterized by the kernel, or \textit{zero modes} (0-modes) of $\var{S}$, \textbf{again up to boundary terms at $\Sigma^\pm$}.

@@

	Compared to the definition of $\tilde{\mcal{P}}$, namely $\var{S}|_{\tilde{\mcal{P}}}$ vanishes up to $\Sigma^\pm$ terms, we see that for a symmetry $\xi$, $X_\xi$ is always tangent to $\tilde{\mcal{P}}$, so that the restriction of the off-shell $\var_\xi \phi$ to on-shell $\tilde{\mcal{P}}$ is well-defined, as expected.

	To finally arrive at Noether's theorem, we note that:
	\begin{equation}
		\var_\xi S|_{\tilde{\mcal{P}}}
		= (X_\xi \cdot \var{S})\big|_{\tilde{\mcal{P}}}
		= X_\xi \cdot (\var{S}|_{\tilde{\mcal{P}}})
		= \int_{\Sigma^\pm} ({\cdots})
	\end{equation}
	Namely, the \textbf{on-shell symmetry variation}, which is generally \textbf{non-zero} but vanishes up to $\Sigma^\pm$ terms, can be obtained in two ways: by first computing the off-shell symmetry variation $\var_\xi S$ and then restricting it on shell, or by first computing the on-shell variation $\var{S}|_{\tilde{\mcal{P}}}$ and then inserting the symmetry. We should get the same result either way, which means that:
	\begin{equation}
		0 = X_\xi \cdot (\var{S}|_{\tilde{\mcal{P}}})
		- (X_\xi \cdot \var{S})\big|_{\tilde{\mcal{P}}}
		= \int_{\Sigma^\pm} ({\cdots})
		= \pqty{
				\int_{\Sigma^+} - \int_{\Sigma^-}
			}\, ({\cdots})
		= H_\xi^+ - H_\xi^-
	\label{eq:charge_conserve_schematic}
	\end{equation}

>>>>

% !TeX TS-program = pdflatex
% !TeX document-id = {b5392a94-51a3-49d1-9ba5-698bc09f9d35}
% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %

@@

\input{../preamble.tex}
\input{../.modules/basics/biblatex.tex}
\input{../.modules/basics/theorem.tex}

\declaretheorem[
	numbered=no
	,style=nonumber
	,name=Remark
]{remark*}

@@

\addtocounter{section}{-1}
\section{Introduction \& Conventions}
	The phase space is understood as the space of \textit{all solutions} of the equations of motion (EoMs), satisfying the boundary conditions. Alternatively, we can think of it as a collection of all possible \textit{initial configurations} of the system, and the additional \textit{symplectic structure} specifies their evolutions. This idea is best explained by \textcite{Crnkovic:1986ex}.

@@

	\begin{itemize}
	\item $\mcal{F}$ denotes the field space including \textbf{off-shell} configurations: $\phi^I$,\\
	and also \textbf{background fields} $\phi^B$; \\
	the variation $\delta$ is assumed to be off-shell unless otherwise specified.

	\item $\tilde{\mcal{P}}$ denotes the field space including \textbf{on-shell} configurations only; \\
	one can then define a symplectic form $\omega$ on $\tilde{\mcal{P}}$, \\
	but it might be degenerate due to gauge redundancies.

	\item $\mcal{P}$ denotes the \textbf{physical phase space}, \\
	with background fields turned off: $\var{\phi^B}|_{\mcal{P}} = 0$, \\
	and with a ``physical'' (non-degenerate) sympletic structure

	\item The index $I$ labels \textbf{all fields} in the theory, \\
	including non-dynamical \textbf{background fields}, \\
	which is labeled by the index $B$.

@@

	\end{itemize}
%\smallskip
\textit{Diffeomorphism and the stress tensor:}

	\begin{itemize}
	\item A infinitesimal diffeomorphism (diffeo) generated by vector field $\xi$ is given by:
	\begin{equation}
		x\mapsto x - \xi,
	\quad
		\var_\xi \phi
		= X_\xi \cdot \var{\phi}
		= +\ldv{\xi} \phi,
	\label{eq:diffeo_convention}
	\end{equation}
	Here the sign convention is chosen such that $\var_\xi \phi$ corresponds to a positive Lie derivative along $\xi$. Note that \textcite{Banados:2016zim} picks a unconventional Lie derivative which contains a minus sign in its definition; we are \textit{not} going to follow that. In this convention the usual current for spacetime translation is given by:
	\begin{equation}
	\begin{aligned}
		\xi &= -\pdd{\sigma},
	&
		j^\mu_\xi
		&= j^\mu_{-\pdd{\sigma}}
		= T^{\mu\nu} \eta_{\nu\sigma}
		= T^{\mu\nu} (\pdd{\sigma})_\nu,
%	\\
%		\xi &= -\epsilon
%		= -\epsilon^\sigma \pdd{\sigma},
%	\quad
%	&
%		j^\mu_\xi
%		&= \epsilon^\sigma j^\mu_{-\pdd{\sigma}}
%		= \epsilon_\nu T^{\mu\nu}
%		= \epsilon^\nu T\id{^\mu_\nu},
	\end{aligned}
	\label{eq:Noether_stress_convention}
	\end{equation}
	Where $T^{\mu\nu}$ is the Noether stress tensor.

	\item Wick rotation between Lorentzian and Euclidean signatures is defined such that:
	\begin{equation}
		\tau = it,
	\quad
		V^0_E = iV^0_L,
	\quad
		(\dd[D]{x})_E
		= i\,(\dd[D]{x})_L,
	\quad
		e^{iS_L} = e^{-S_E},
	\quad
		\mcal{L}_E
		= -\mcal{L}_L
	\label{eq:Wick_rotation}
	\end{equation}
	Where $
		S = \int \dd[D]{x} \sqrt{\abs{g}}\,\mcal{L}
	$ in both cases, and $V^0$ is the 0-th component of some $V^\mu$. Other scalar quantities, such as $
		g_{\mu\nu} V^\mu W^\nu
	$, are left invariant. This is the convention introduced in \textcite{Polchinski:1998rq}, Appendix A. 
	For example, the Einstein-Hilbert action is given by\footnote{
		For a closed Riemann surface in 2D, by Gauss--Bonnet theorem, we see that the Euclidean action is proportional to genus of the surface:
		\begin{equation}
			S_E = -\frac{1}{16\pi G_N}\,
				4\pi \chi(M)
			= -\frac{1}{4G_N}\,\chi(M),
		\quad
			\chi(M) = 2 - 2g,
		\quad
			e^{-S_E}
			\propto e^{-\frac{1}{2G_N} g}
		\end{equation}
		Note that in \textcite{Polchinski:1998rq}, the dilaton term in the Euclidean worldsheet action  goes like $+R\,\Phi(X)$, namely it's missing the minus sign; this is due to the convention for the dilaton $\Phi$: in the perturbative regime we have $\ave{\Phi} = \lambda < 0$, and thus $
			e^{-S_E} \sim e^{-\lambda \chi}
			\sim (g_c^2)^g
		$, where $
			g_c \sim e^\lambda < 1
		$ is the closed string coupling. 
	}:
	\begin{equation}
		S_L = \frac{1}{16\pi G_N}
			\int \sqrt{-g} \dd[D]{x} R,
	\quad
		S_E = -\frac{1}{16\pi G_N}
			\int \sqrt{g} \dd[D]{x} R
	\end{equation}

@@

	\item The Hilbert stress tensor is defined with the Lorentzian action:
	\begin{equation}
		T_{\mu\nu}(x)
		= - \frac{2}{\sqrt{-g}}
			\fdv{S_L}{g^{\mu\nu}(x)},
	\quad
		T^{\mu\nu}(x)
		= + \frac{2}{\sqrt{-g}}
			\fdv{S_L}{g_{\mu\nu}(x)}
	\end{equation}\\[-1.25\baselineskip]
	\begin{equation}
		\var{S_L}
		= \int \sqrt{-g} \dd[D]{x} 
			\pqty{
				-\frac{1}{2}\, T_{\mu\nu}
				\var{g^{\mu\nu}}
				+ \cdots
			}
		= \int \sqrt{-g} \dd[D]{x} 
			\pqty{
				+\frac{1}{2}\, T^{\mu\nu}
				\var{g_{\mu\nu}}
				+ \cdots
			}
	\end{equation}
	To understand the variational derivative here, we note that in the space of fields it's convenient to think of $x$ as an index to be contracted; the contraction is implemented by $
		\int \dd[D]{x}
	$, without the $\sqrt{\abs{g}}$ factor\footnote{
		An action can thus be thought of as the contraction between some fields and some operators with multiple $x$ ``indices'': $\Box_{x,x',\cdots}$. For example, we might have some bi-local operator $\Box_{x,x'}$ connecting $\phi(x)$ and $\phi(x')$. 
		In a \textit{local} action all these operators should be \textit{diagonal} in $x$, i.e.~$
			\Box_{x,x'} = \delta^D(x - x')\,\Box_x
		$. 
	}.

@@

\pagebreak[4]
\section{Covariant formalism and Noether's theorem}
\subsection{Off-shell variation on the field space}
	\noindent
	Let's start by considering a general action with boundary terms \cite{Harlow:2019yfa}:
	\begin{equation}
		S = \int_M L + \int_{\pd M} l,
	\quad
		L = \dd[D]{x} \sqrt{\abs{g}}\,\mcal{L}
	\end{equation}

	Variation $\var$ is now treated as an \textit{exterior derivative} on the space of fields. We can think of it as an \textit{enlarged} space with \textit{redundant variables} $(\pi_\mu,\phi)_I$, where $I$ labels all fields in the system. We have:
	\begin{equation}
		\var{S}
		= \int_M \var{L}
			+ \int_{\pd M} \var{l}
		= \int_M E_I \var{\phi^I}
			+ \int_{\pd M} \pqty{\Theta + \var{l}},
	\end{equation}
	We've defined $\Theta$ which comes from the total derivative terms of the bulk $M$ variation, and we've performed an integration by parts and reduced $\int_M \dd{\Theta} = \int_{\pd M} \Theta$. Basically,
	\begin{empheq}{equation}
		\var{L}
		= E_I \var{\phi^I} + \dd{\Theta}
	\end{empheq}
	\vspace{-.3\baselineskip}
	\begin{equation}
		({\cdots})_I \var{(\dd{\phi^I})}
		= ({\cdots})_I \dd{(\var{\phi^I})}
		\sim \dd{(\cdots \var{\phi})}
		= \dd{\Theta},
	\quad
		\Theta \sim ({\cdots})_I \var{\phi^I}
	\end{equation}

@@

	Note that $\mcal{F}$ \textbf{includes possible ``background'' fields $\phi^B$} such as the static metric $g^{\mu\nu}$ for a field theory defined on a curved spacetime. These fields are fixed on-shell and therefore are absent in $\mcal{P}$. A proper treatment of background fields is nicely summarized by \textcite{Banados:2016zim}, but we will take a slightly different approach, as we shall see later.

@@

	What we've done here is simply a rewrite of the usual variation procedure; we just re-think it as a differential in the field space. To get to the physical phase space, we
%	\textbf{suppress the variation of background fields $\phi^B$}, and then 
	require the action to be \textbf{stationary, up to
	variation of the background fields, and
	up to terms in the future / past boundary $\Sigma^\pm$:}
	\begin{empheq}{equation}
%		\var{\phi^B}|_{\tilde{\mcal{P}}}
%		= 0,
%	\quad
		\var{S}|_{\tilde{\mcal{P}}}
		= \int_M E_B \var{\phi^B}
			+ \int_{\Sigma^+} ({\cdots})
			- \int_{\Sigma^-} ({\cdots})
		= \int_M E_B \var{\phi^B}
			+ \int_{\Sigma^\pm} ({\cdots})
	\end{empheq}

	This differs slightly from what we are used to in most physics literature, where we simply set $\var{S} = 0$ to find the EoMs. The reason is that in physics, we usually \textit{impose} the initial \& final conditions, or in other words, in \& out states, and the variation at $\Sigma^\pm$ is \textit{required} to vanish: $\var{\phi}|_{\Sigma^\pm} = 0$. 
	Consider the simplest example: the (0+1)\,D worldline action of a point particle; we have:
	\begin{equation}
		S = \int L = \int \dd{t} \mcal{L},
	\quad
		\var{S}
		= \int E_I(t) \var{q^I(t)}
			+ \Theta\big|^{\Sigma^+}_{\Sigma^-}
	\end{equation}
	\vspace{-.5\baselineskip}
	\begin{equation}
		E_I = \pqty{
			\pdv{\mcal{L}}{q^I}
			- \dv{t} \pdv{\mcal{L}}{\dot{q}^I}
		} \dd{t},
	\quad
		\Theta
		= \pdv{\mcal{L}}{\dot{q}^I} \var{q^I}
		= p_I \var{q^I},
	\quad
		p_I = \pdv{\mcal{L}}{\dot{q}^I}
	\end{equation}
	Traditionally, we impose $\var{q^I}|_{\Sigma^\pm} = 0$ as we fix the in \& out states, and then we find the EoMs $E_I = 0$. 
	Same applies to the background field variation, where we simply set $\var{\phi^B} = 0$. 
	However, this is slightly clumsy to implement in our new language, since $\var{\phi}$ is now a differential form in the phase space. We thus simply require that $\var{S}|_{\tilde{\mcal{P}}}$ vanish up to boundary terms at $\Sigma^\pm$, which achieve the same result.

	Generally, we have:
	\begin{equation}
		\var{S}|_{\tilde{\mcal{P}}}
		= \int_M E_B \var{\phi^B}
			+ \int_{\Sigma^\pm} ({\cdots})
	\quad\Longrightarrow\quad
		E_{I\ne B}|_{\tilde{\mcal{P}}} = 0,
	\quad
		\int_N \pqty{\Theta + \var{l}}_{\tilde{\mcal{P}}}
		= \int_{\Sigma^\pm} ({\cdots}),
	\end{equation}
	\vspace{-.8\baselineskip}
	\begin{equation}
		\pd M = N \cup \Sigma^+ \cup (-\Sigma^-),
	\end{equation}
	Here $N$ is the spatial boundary. 
	In this way we've obtained the subspace (submanifold) $\tilde{\mcal{P}}$ of \mbox{solutions} constrained by the EoMs. We are one step closer to the physical phase space; in fact this \textit{is} the physical phase space $\mcal{P}$ if there are no gauge redundancies in the fields, and the variation of background fields are turned off: $\var{\phi^B} = 0$.

	Besides the EoMs, the boundary integral at $N$ should also vanish; this means that \textbf{not all boundary conditions are consistent with the theory}. 
	In fact, $N$ is where the dual theory lives for many holographic systems, so one would imagine that it's highly non-trivial. Generally \cite{Harlow:2019yfa},
	\begin{empheq}{gather}
		(\Theta + \var{l})_{\tilde{\mcal{P}},N}
		= \dd{C},
	\quad
		\dd{C}\colon\ %
		\text{some 1-form on $N \subset \pd M$},
	\label{eq:boundary_cond}
	\\
	\Longrightarrow\ %
		\int_{N} (\Theta + \var{l})_{\tilde{\mcal{P}}}
		= \int_{\pd M} \dd{C}
			+ ({\cdots})
		= \int_{\pd \pd M = \varnothing} C
			+ ({\cdots})
		= 0
			+ \int_{\Sigma^\pm} ({\cdots})
	\end{empheq}

@@

	We shall see that this formalism will help us avoid confusions with boundary terms, which is best explained by \textcite{Banados:2016zim}. Also, off-shell variation will be quite useful if we want to quantize our theory, where we have to integrate over off-shell configurations as well. 
\subsection{Symmetry variation and the Noether current}
	To get back to the familiar Noether's procedure, we need only plug in (contract with) a vector field $X_\xi$ in the field space $\mcal{F}$, labeled by the symmetry $\xi$:
	\begin{equation}
		\var_\xi
		= X_\xi \cdot \var
		= \iota_{X_\xi} \var
	\colon\ \Omega^0_\delta(\mcal{F})
		\to \Omega^0_\delta(\mcal{F})
	\end{equation}
	$\xi\mapsto X_\xi$ is the representation of $\xi$ in the field space, and $\Omega^0_\delta(\mcal{F})$ denotes 0-forms, i.e.~functions on $\mcal{F}$. 
	As an example, for diffeomorphism (diffeo), the induced variation is given by:
	\begin{equation}
		x\mapsto x - \xi,
	\quad
		\var_\xi \phi
		= X_\xi \cdot \var{\phi}
		= \ldv{\xi} \phi,
	\quad
		X_\xi
		= \int_M \dd[D]{x}
			\pqty\big{\ldv{\xi} \phi^I(x)}
			\fdv{\phi^I(x)}
	\label{eq:symmetry_var_field}
	\end{equation}

@@

	By now we've written down the above expressions \eqref{eq:symmetry_var_field} covariantly on the off-shell field space $\mcal{F}$, in terms of the redundant coordinates $\phi^I$. However, we can still interpret it as a variation on $\tilde{\mcal{P}}$, by simple restriction.

	In fact, by the definition of a \textit{symmetry} $\xi$, we have the \textbf{off-shell symmetry variation}:
	\begin{empheq}{equation}
		\var_\xi S = X_\xi \cdot \var{S}
		= \int_{\Sigma^\pm} ({\cdots})
	\end{empheq}
	In other words, the action of symmetries in the field space is characterized by the kernel, or \textit{zero modes} (0-modes) of $\var{S}$, \textbf{again up to boundary terms at $\Sigma^\pm$}.

@@

	Also, here we \textbf{do allow ``generalized'' symmetries to act no-trivially on the background fields $\phi^B$}, but it has to combine with other variations and altogether reduce to some boundary terms at $\Sigma^\pm$. This is different from the treatment of \textcite{Banados:2016zim}, but it will prove to be convenient when we deal with background gauge fields, such as a background metric.

	Intuitively, the generalized symmetries which act non-trivially on the background fields come from some ``true'' symmetries in a larger system $\hat{S}$, where the fields $\phi^B$ are dynamically \textit{turned on}. A prominent example is again, the static background metric $g^{\mu\nu}$ for a field theory on a curved spacetime. General diffeomorphism is \textit{not} truly a symmetry of the theory, since it disturbs the background metric; however, it is truly a (gauge) symmetry when we turn on dynamic $g^{\mu\nu}$. We will come back to this example shortly.

	\newparagraph
	Compared to the definition of $\tilde{\mcal{P}}$, namely $\var{S}|_{\tilde{\mcal{P}}}$ vanishes up to $\var{\phi^B}$ and $\Sigma^\pm$ terms, we see that for a symmetry $\xi$, $X_\xi$ is always tangent to $\tilde{\mcal{P}}$, so that the restriction of the off-shell $\var_\xi \phi$ to $\tilde{\mcal{P}}$ (on-shell) is well-defined, as expected.

\pagebreak

	To finally arrive at Noether's theorem, we note that:
	\begin{equation}
		\var_\xi S|_{\tilde{\mcal{P}}}
		= (X_\xi \cdot \var{S})\big|_{\tilde{\mcal{P}}}
		= X_\xi \cdot (\var{S}|_{\tilde{\mcal{P}}})
		= \int_M E_B \,\var_\xi{\phi^B}
			+ \int_{\Sigma^\pm} ({\cdots})
	\end{equation}
	Namely, the \textbf{on-shell symmetry variation}, which is generally \textbf{non-zero} but vanishes up to $\Sigma^\pm$ terms, can be obtained in two ways: by first computing the off-shell symmetry variation $\var_\xi S$ and then restricting it on shell, or by first computing the on-shell variation $\var{S}|_{\tilde{\mcal{P}}}$ and then inserting the symmetry. We should get the same result either way, which means that:
	\begin{equation}
	\begin{aligned}
		0
		= X_\xi \cdot (\var{S}|_{\tilde{\mcal{P}}})
		- (X_\xi \cdot \var{S})\big|_{\tilde{\mcal{P}}}
		&= \int_M E_B \,\var_\xi{\phi^B}
			+ \int_{\Sigma^\pm} ({\cdots}) \\
		&= \int_M E_B \,\var_\xi{\phi^B}
			+ \pqty{
				\int_{\Sigma^+} - \int_{\Sigma^-}
			}\, ({\cdots}) \\
		&= \int_M E_B \,\var_\xi{\phi^B}
			+ H_\xi^+ - H_\xi^-
	\end{aligned}
	\label{eq:charge_conserve_schematic}
	\end{equation}
